A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-28 4_method.tex
change b~ b- b^ to \tilde{b} \bar{b} \hat{b}

As depicted in \cref{3d_surface_overview_center}, our method first identifies edges and nodes in the skeleton that are located in the center of the polygon, which correspond to ridges and peaks in the UoC  (\cref{sec_center_classification}).
The heights $b^\sim$ at these elements are then quantized to an integer number of beads $b^\neg$.
To ensure a smooth toolpath between regions with quantized integer heights that differ, we add new nodes in the skeleton with quantized heights and interpolate the heights $b^\wedge$ in between (\cref{sec_central_height_adjustment}).
The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain toolpaths with varying spacing, which translates into varying width (\cref{sec_toolpath_extraction}).

@@

%\subsubsection{Union of cones}
\paragraph{Approximation of union of cones}
The skeleton trapezoidation (ST) provides a means to visualize the union of cones (UoC) approximated by a 3D surface mesh composed of quadrilateral and triangular patches.
%In order to visualize the ST as a 3D surface, we add a third dimension.
We assign each node in ST a (real number) height value measured in terms of beads, referred to as the \emph{bead count} $b$.
We define the bead count as the number of beads to fit along the \emph{diameter} of the inscribed circle centered at node $v$, i.e. $2R(v)$, by
\begin{equation}
    b^\sim_v = 2 R(v) / w^*
\label{eq:initialBeadCount}
\end{equation}
where $w^*$ is the nozzle size. 
%While the feature radii are measured along the support edges, the diameter is not measurable as such because the support edges are generally not collinear;
We divide the diameter rather than the radius as this allows to deal with an odd number of beads while using integer logic.
%The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
Note that although the overview of the method has been described geometrically in terms of the UoC, the actual toolpath generation relies on the two-dimensional ST, while the use of the bead count as a height value is only a visualization aid.

@@

\subsection{Central height adjustment}\label{sec_central_height_adjustment}
Now that we have identified and marked the central regions we quantize their heights.
We first quantize the initial bead count $b^\sim$ into an integer bead count $b^\neg$ at the marked nodes using a quantization operator $q$,
then find the locations along the edges where $q$ makes a jump from one bead count $n$ to another $n+1$
and then introduce ramps to smoothly transition from $n$ to $n+1$ using fractional bead counts $b^\wedge$ along the smooth transition.
%\subsubsection{Initial bead count}\label{sec_initial_bead_count}

@@

\paragraph{Quantization}
We define a quantization operator $q$ to map a feature diameter ($d=2R(v)$) to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
Because our quantization scheme should round to the nearest integer multiple of the nozzle size, we have
$q(d) = \left\lfloor d / w^* + \nicefrac12 \right\rfloor$.
Alternative quantization schemes will be discussed in \cref{sec_generalization}.
By applying $q$ to the heights of central nodes we quantize the bead count:
\begin{equation}\label{eq_quantized_bead_count}
b^\neg_v = q(2R(v)) = \left\lfloor b^\sim_v + \nicefrac12 \right\rfloor
\end{equation}

@@

\paragraph{Transition anchors}
For a marked edge which connects nodes $v_0$ and $v_1$ with $b^\neg_{v_0} \le n < b^\neg_{v_1}$, we determine the \emph{transition anchor locations} at which the bead count transitions from $n$ to $n+1$.
To this end, we introduce the function 
\begin{equation}
    q^{-1}(n) := \argmax_d q(d) = n,
\end{equation}
which gives the feature diameter $d$ at which the bead count $q$ transitions from $n$ to $n+1$.
The location of the anchor $v_x$ is then computed by inversely interpolating $R(v_x) = q^{-1}(n)$, i.e. 
\begin{equation}
    v_x = v_0 + (v_1 - v_0) \frac{ q^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }.
\end{equation}
%for each $n$ such that $b^*_{v_0}\le n<b^*_{v_1}$.
An illustration of the anchors is shown in \cref{beading_transitioning_filtering__transition_mids}.

@@

A sharp transition from $n$ to $n+1$ beads at an anchor location creates sharp turns in the toolpath (see \cref{transitions} top).
A transition length $t(n)$ is introduced to ensure a smooth transition (see \cref{transitions}). 
The length of the transition is set to $t(n) = w^*$ and it is centered at the anchor, i.e. the distance from the lower end $v_0$ to the anchor position $v_x$ is set to
$t_0(n) = \Delta(v_0v_x) = \nicefrac12 w^*$, 
where $\Delta$ is the total distance along the edges in between two nodes.
We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
In order to make the transition ramps robust against small perturbations in the outline shape, we modify the nodes $v_x$ which are in between the two ends $v_0$ and $v_1$ of the transition by (re-)assigning them a fractional bead count $b^\wedge$ which is linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}):
\begin{equation}
b^\wedge_{v_x} = n + {\Delta(v_0v_x)} / {\Delta(v_0v_1)}
\end{equation}
%This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});
%compare the top and bottom of \cref{beading_transitioning_filtering}. 
Finally we update the ST by adding support edges at the transition ends. 
As shown in \cref{beading_transitioning_filtering__result_uoc}, the marked regions in the UoC mesh have become horizontal at integer multiples of $\nicefrac12 w^*$ for long stretches with ramps in between.

@@

\paragraph{Beading} 
We associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
For our distributed beading scheme we define the beading for a central node $v$ with $n = b^\wedge_v$ beads and a diameter $d = 2R(v)$  as:
\begin{align*}
    B(n,d) &= \left( W(n,d), L(n,d) \right)   &=   \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right) \\
    w_i &= 2R(v) / n  & \text{for all $i < n$}\\
    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i < n$}
\end{align*}
where
$w_i$ and $l_i$ are the width and location of the $i$th bead,
respectively, counting from the outline inward.
An example beading is visualized in the top of \cref{beading_interpolation}:
$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.

@@

\begin{algorithm}
\caption{Beading propagation}
\label{alg_beading_propagation}
\begin{algorithmic}
\ForAll{$v \in$ nodes}
	\If {marked($v$)} $\text{map}[v] = (0, B(b^\wedge_v, 2 R(v)))$ \EndIf
\EndFor
\ForAll{$e \in$ edges}
	\If {$R(v_0^e) < R(v_1^e)$}
		% \State 
		upwardEdges.add($e$)
	\EndIf
\EndFor
\State upwardEdges.sort($\uplambda e_1 e_2 . R(v_1^{e_1}) < R(v_1^{e_2})$) \Comment {low to high $v_1$}
\ForAll{$e \in$ upwardEdges} \Comment{upward phase}
	\If {$\text{map}[v_0^e] \land \neg \text{map}[v_1^e$]}
    		\State $(d, B) = \text{map}[v_0^e]$
    		\State $\text{map}[v_1^e] \leftarrow (d + |v_1^e - v_0^e|, B)$
	\EndIf
\EndFor
\ForAll{$e \in$ reverse(upwardEdges)} \Comment{downward phase}
	\If {$\text{map}[v_1^e]$}
    		\State $(d, B) \leftarrow \text{map}[v_1^e]$
    		% d + |v_1^e - v_0^e|
    		\If {$\text{map}[v_0^e]$}
    			\State $(d_0, B_0) = \text{map}[v_0^e]$
    			\State $B \leftarrow \text{interpolate}(\min(1, d_0 /  t_\text{beading}), B_0, B)$
    		\EndIf
    		\State $\text{map}[v_1^e] \leftarrow (0, B)$
	\EndIf
\EndFor
\end{algorithmic}
\end{algorithm}

@@

Because the bead count is defined in terms of the feature diameter rather than the radius, only some of the bead count values $b^\wedge$ in a central region coincide with a slicing height.
When the bead count $b^\wedge$ is even, the ridge will be sliced as normal;
the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
When the bead count $b^\wedge$ is odd, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.
In that case we should prevent the algorithm from generating the center extrusion segment twice from the trapezoids on either side of that segment.
We therefore use some arbitrary condition to decide which one of the two to include based on the ordering of the coordinates of $v_0$ and $v_1$: $x_0 < x_1 \lor (x_0 = x_1 \land y_0 < y_1)$.

>>>>

As depicted in \cref{3d_surface_overview_center}, our method first identifies edges and nodes in the skeleton that are located in the center of the polygon, which correspond to ridges and peaks in the UoC  (\cref{sec_center_classification}).
The heights $\tilde{b}$ at these elements are then quantized to an integer number of beads $\bar{b}$.
To ensure a smooth toolpath between regions with quantized integer heights that differ, we add new nodes in the skeleton with quantized heights and interpolate the heights $\hat{b}$ in between (\cref{sec_central_height_adjustment}).
The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain toolpaths with varying spacing, which translates into varying width (\cref{sec_toolpath_extraction}).

@@

%\subsubsection{Union of cones}
\paragraph{Approximation of union of cones}
The skeleton trapezoidation (ST) provides a means to visualize the union of cones (UoC) approximated by a 3D surface mesh composed of quadrilateral and triangular patches.
%In order to visualize the ST as a 3D surface, we add a third dimension.
We assign each node in ST a (real number) height value measured in terms of beads, referred to as the \emph{bead count} $b$.
We define the bead count as the number of beads to fit along the \emph{diameter} of the inscribed circle centered at node $v$, i.e. $2R(v)$, by
\begin{equation}
    \tilde{b}_v = 2 R(v) / w^*
\label{eq:initialBeadCount}
\end{equation}
where $w^*$ is the nozzle size. 
%While the feature radii are measured along the support edges, the diameter is not measurable as such because the support edges are generally not collinear;
We divide the diameter rather than the radius as this allows to deal with an odd number of beads while using integer logic.
%The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
Note that although the overview of the method has been described geometrically in terms of the UoC, the actual toolpath generation relies on the two-dimensional ST, while the use of the bead count as a height value is only a visualization aid.

@@

\subsection{Central height adjustment}\label{sec_central_height_adjustment}
Now that we have identified and marked the central regions we quantize their heights.
We first quantize the initial bead count $\tilde{b}$ into an integer bead count $\bar{b}$ at the marked nodes using a quantization operator $q$,
then find the locations along the edges where $q$ makes a jump from one bead count $n$ to another $n+1$
and then introduce ramps to smoothly transition from $n$ to $n+1$ using fractional bead counts $\hat{b}$ along the smooth transition.
%\subsubsection{Initial bead count}\label{sec_initial_bead_count}

@@

\paragraph{Quantization}
We define a quantization operator $q$ to map a feature diameter ($d=2R(v)$) to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
Because our quantization scheme should round to the nearest integer multiple of the nozzle size, we have
$q(d) = \left\lfloor d / w^* + \nicefrac12 \right\rfloor$.
Alternative quantization schemes will be discussed in \cref{sec_generalization}.
By applying $q$ to the heights of central nodes we quantize the bead count:
\begin{equation}\label{eq_quantized_bead_count}
\bar{b}_v = q(2R(v)) = \left\lfloor \tilde{b}_v + \nicefrac12 \right\rfloor
\end{equation}

@@

\paragraph{Transition anchors}
For a marked edge which connects nodes $v_0$ and $v_1$ with $\bar{b}_{v_0} \le n < \bar{b}_{v_1}$, we determine the \emph{transition anchor locations} at which the bead count transitions from $n$ to $n+1$.
To this end, we introduce the function 
\begin{equation}
    q^{-1}(n) := \argmax_d q(d) = n,
\end{equation}
which gives the feature diameter $d$ at which the bead count $q$ transitions from $n$ to $n+1$.
The location of the anchor $v_x$ is then computed by inversely interpolating $R(v_x) = q^{-1}(n)$, i.e. 
\begin{equation}
    v_x = v_0 + (v_1 - v_0) \frac{ q^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }.
\end{equation}
%for each $n$ such that $b^*_{v_0}\le n<b^*_{v_1}$.
An illustration of the anchors is shown in \cref{beading_transitioning_filtering__transition_mids}.

@@

A sharp transition from $n$ to $n+1$ beads at an anchor location creates sharp turns in the toolpath (see \cref{transitions} top).
A transition length $t(n)$ is introduced to ensure a smooth transition (see \cref{transitions}). 
The length of the transition is set to $t(n) = w^*$ and it is centered at the anchor, i.e. the distance from the lower end $v_0$ to the anchor position $v_x$ is set to
$t_0(n) = \Delta(v_0v_x) = \nicefrac12 w^*$, 
where $\Delta$ is the total distance along the edges in between two nodes.
We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
In order to make the transition ramps robust against small perturbations in the outline shape, we modify the nodes $v_x$ which are in between the two ends $v_0$ and $v_1$ of the transition by (re-)assigning them a fractional bead count $\hat{b}$ which is linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}):
\begin{equation}
\hat{b}_{v_x} = n + {\Delta(v_0v_x)} / {\Delta(v_0v_1)}
\end{equation}
%This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});
%compare the top and bottom of \cref{beading_transitioning_filtering}. 
Finally we update the ST by adding support edges at the transition ends. 
As shown in \cref{beading_transitioning_filtering__result_uoc}, the marked regions in the UoC mesh have become horizontal at integer multiples of $\nicefrac12 w^*$ for long stretches with ramps in between.

@@

\paragraph{Beading} 
We associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
For our distributed beading scheme we define the beading for a central node $v$ with $n = \hat{b}_v$ beads and a diameter $d = 2R(v)$  as:
\begin{align*}
    B(n,d) &= \left( W(n,d), L(n,d) \right)   &=   \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right) \\
    w_i &= 2R(v) / n  & \text{for all $i < n$}\\
    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i < n$}
\end{align*}
where
$w_i$ and $l_i$ are the width and location of the $i$th bead,
respectively, counting from the outline inward.
An example beading is visualized in the top of \cref{beading_interpolation}:
$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.

@@

\begin{algorithm}
\caption{Beading propagation}
\label{alg_beading_propagation}
\begin{algorithmic}
\ForAll{$v \in$ nodes}
	\If {marked($v$)} $\text{map}[v] = (0, B(\hat{b}_v, 2 R(v)))$ \EndIf
\EndFor
\ForAll{$e \in$ edges}
	\If {$R(v_0^e) < R(v_1^e)$}
		% \State 
		upwardEdges.add($e$)
	\EndIf
\EndFor
\State upwardEdges.sort($\uplambda e_1 e_2 . R(v_1^{e_1}) < R(v_1^{e_2})$) \Comment {low to high $v_1$}
\ForAll{$e \in$ upwardEdges} \Comment{upward phase}
	\If {$\text{map}[v_0^e] \land \neg \text{map}[v_1^e$]}
    		\State $(d, B) = \text{map}[v_0^e]$
    		\State $\text{map}[v_1^e] \leftarrow (d + |v_1^e - v_0^e|, B)$
	\EndIf
\EndFor
\ForAll{$e \in$ reverse(upwardEdges)} \Comment{downward phase}
	\If {$\text{map}[v_1^e]$}
    		\State $(d, B) \leftarrow \text{map}[v_1^e]$
    		% d + |v_1^e - v_0^e|
    		\If {$\text{map}[v_0^e]$}
    			\State $(d_0, B_0) = \text{map}[v_0^e]$
    			\State $B \leftarrow \text{interpolate}(\min(1, d_0 /  t_\text{beading}), B_0, B)$
    		\EndIf
    		\State $\text{map}[v_1^e] \leftarrow (0, B)$
	\EndIf
\EndFor
\end{algorithmic}
\end{algorithm}

@@

Because the bead count is defined in terms of the feature diameter rather than the radius, only some of the bead count values $\hat{b}$ in a central region coincide with a slicing height.
When the bead count $\hat{b}$ is even, the ridge will be sliced as normal;
the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
When the bead count $\hat{b}$ is odd, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.
In that case we should prevent the algorithm from generating the center extrusion segment twice from the trapezoids on either side of that segment.
We therefore use some arbitrary condition to decide which one of the two to include based on the ordering of the coordinates of $v_0$ and $v_1$: $x_0 < x_1 \lor (x_0 = x_1 \land y_0 < y_1)$.
